### 2015-10-26 vmcai-2016-tex/approach.tex
Changes with Ben
Added forward references to VS and ST functions.

There are three sets of rewrite
rules specific to the~\symtxt{} algorithm: (i) rules to initialize
symbolic references, (ii) rules to perform field dereferences and
writes, and (iii) rules to check equality and inequality of
references.

@@

There are two rewrite rules in~\figref{fig:fHeap}, one for reading
the value of a field (field-access) and the other for writing to a
field (field-write). Both rules first check that the operations can be
performed on a non-null location. The field-access rewrite rule
in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
uses \figref{fig:symInit}, to get a new symbolic heap that is
initialized on the field $\cfgnt{f}$. The symbolic heap is further
modified to include a new stack reference pointing to the guarded value set
(possible values of the field) returned during the dereferencing; the
new stack reference is the return value from the $\mathbb{VS}$ operation.

>>>>

There are three sets of rewrite
rules specific to the~\symtxt{} algorithm: (i) rules to initialize
symbolic references, (ii) rules to perform field dereferences and
writes, and (iii) rules to check equality and inequality of
references. Rules relating to (ii) and (iii) are similar to previously proposed methods utilizing guarded value sets \cite{Sen:2014,Dillig:2011}. The rules for (i) are novel in how they  preserve \gsetxt\ semantics.

@@

Certain rewrite rules depend on auxiliary on the relations in \defref{def:VS} and \defref{def:ST}, such as those in~\figref{fig:fHeap}. There are two rewrite rules in~\figref{fig:fHeap}, one for reading
the value of a field (field-access) and the other for writing to a
field (field-write). Both rules first check that the operations can be
performed on a non-null location. The field-access rewrite rule
in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
uses \figref{fig:symInit}, to get a new symbolic heap that is
initialized on the field $\cfgnt{f}$. The symbolic heap is further
modified to include a new stack reference pointing to the guarded value set
(possible values of the field) returned during the dereferencing; the
new stack reference is the return value from the $\mathbb{VS}$ operation.
